The title

### 2016-10-03 analysis/paper/paper.Rmd
update pkgs
regional structural geology

@@

```{r}

```

>>>>

The study area is located between the Sagaing fault to the west and the Shan scarp to the east. The Sagaing fault is a major strike-slip right-lateral continental fault that extends over 1200 km, first described by Noetling [-@noetling1900miocene], and later described by others [e.g. @thein1991lateral; maung1987transcurrent]. The Shan scarp is a topographic discontinuity that marks the boundary of the central plains and the Shan plateau to the east, a region with an average elevation of 1000 m and large variations of elevation over short distances (up to 1800 m over a few kilometers) [@bertrand2001diachronous; bertrand2003tectonics].

@@

```{r}
# analysis of survey and GPS data in here
```
